Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-01-31 cogsci/cogsci.tex
modif cogsci draft

\begin{abstract}
Children tend to produce words earlier when they are connected to other
words along both the phonological and semantic dimensions. Though this
connectivity effect has been extensively documented, little is known
about the underlying developmental mechanism. One view suggests that
learning is primarily driven by a network growth model where highly
connected words in the child's ealy lexicon attract similar words.
Another view suggests that learning is driven, not by highly connected
words in the early internal lexicon, but by words that are highly
connected in the external learning environment. The present study tests
both scenarios systematically in both the phonological and the semantic
domains, and across 8 languages. We show that external connectivity in
the learning environment drives growth in both the semantic and the
phonological networks, and that this pattern is consistent
cross-linguistically. The findings suggest a word learning mechanism
where children harness their statistical learning abilities to
(indirectly) detect and learn highly connected words in the learning
environment.

@@

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure is best characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words. Previous studies investigated early vocabulary networks
based on different word relations such as shared semantic features,
target-cue relationships in free association norms, co-occurrence in
child directed speech, and phonological similarity. These studies have
found that children tend to produce earlier the words that have higher
neighborhood density (i.e., high connectivity in the network) both at
the phonological and the semantic level (Beckage, Smith, \& Hills, 2011;
Engelthaler \& Hills, 2017; Hills, Maouene, Riordan, \& Smith, 2010;
Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Stella, Beckage, \&
Brede, 2017; Stokes, 2010; Storkel, 2009).

While most studies focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
Steyvers \& Tenenbaum (2005) suggested that the effect of connectivity
is the consequence of how the lexical network gets constructed in the
child's mind. According to this explanation, known as Preferential
Attachment (PAT), highly connected words in the child's lexicon tend to
``attract'' more words over time, in a rich-get-richer scenario
(Barabasi \& Albert, 1999). In other words, what predicts word learning
is the \emph{internal} connectivity in the child's early lexicon. In
contrast, Hills et al. (2009) suggested that what biases the learning is
not the connectivity in the child's internal lexicon but, rather,
\emph{external} connectivity in the learning environment. They called
this alternative explanation Preferential Acquisition (PAC). Figure
\ref{fig:growth} shows an illustration of both growth scenarios with the
same simplified network. These two proposals represent two divergent
ideas about the role of lexical networks in acquisition. On the PAT
proposal, network structure is a causal factor in early word learning;
in contrast, on the PAC approach, network structure is not internally
represented and, therefore, might be an epiphenomenon of the statistics
of the linguisitc input (see discussion).

@@

\caption{\label{fig:growth}Filled circles (I1-I4) represent known words (internal lexicon), and empty circles (E1 and E2) represent words that have not been learned yet (external lexicon). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, each candidate node is characterized with the average degree (i.e., number of links) of the existing nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, each candidate node is characterized with its degree in the entire network. According th PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
\end{figure}
\end{CodeChunk}

Studies that investigate lexical network growth have focused on semantic
networks using English data (Hills et al., 2010, 2009; Steyvers \&
Tenenbaum, 2005). The novelty of the current study is that it
investigates whether phonological networks, like semantic networks, grow
by PAC, or if they rather grow by PAT. It also provides a systematic
comparison of both network growth scenarios in the phonological and the
semantic domains and assesses their relative contribution to the
learning process. Moreover, it tests the generality of the findings
across eight languages.

@@

\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for the phonological network (top) and the semantic network (bottom). Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
\end{figure*}
\end{CodeChunk}

@@

\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
\end{figure*}
\end{CodeChunk}

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). We used the
\emph{Words and Sentence} version of the CDI which contains the
productive vocabulary of toddlers (age varied between 16 to 36 months).
Following previous studies (Hills et al., 2009; e.g., Storkel, 2009), we
restricted our analysis to the category of nouns. The age of acquisition
was defined by the month at which a word was produced by at least 50\%
of children (J. C. Goodman et al., 2008).

We obtained these nouns in eight languages: Croatian, Danish, English,
Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
nouns that had entries in the Florida Association Norms (see below).
Since these norms are available only in English, we used the
hand-checked translation equivalents provided by Braginsky by Braginsky
et al. (2016), allowing us to use the English association norms across
languages. Table \ref{tab:stats} gives an overview of the data used.
Translation equivalents were originally constructed for a subset of
words appearing on the toddler CDI form (the subset is labeled
\emph{Words and Gestures}), and so not all words are currently
available. Note, however, that all languages have at least 60\% of nouns
translated.

@@

Hills et al. (2009), we used as an index of semantic relatedness the
Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
This dataset was collected by giving adult participants a word (the
cue), and asking them to write the first word that comes to mind (the
target). For example, when given the word ``ball'', they might answer
with the word ``game''. A pair of nodes were connected by a directed
link from the cue to the target if there was a cue-target relationship
between these nodes in the association norms. Each node was
characterized by its ``indegree'', which represents the number of links
for which the word was the target. To model growth from month to month,
we constructed a different network at each month, made of words that
have been learned at that month.

@@

We generated approximate International Phonetic Alphabet (IPA)
transcriptions from the orthographic transcription, across languages,
using the open source text-to-speech software
\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
the Levenshtein (edit) distance as a measure of phonological relatedness
between two nodes. The measure counts the minimum number of operations
(insertions, deletions, substitutions) required to change one string
into another.

In previous studies, two nodes were linked if they had an edit distance
of 1 (Stokes, 2010; Storkel, 2009). However, in these previous studies
the network was built using an adult vocabulary. However, since the
children's vocabulary contains very few word pairs with an edit distance
of 1, the resulting networks were too sparse and uninformative. Thus, we
increased the threshold from 1 to 2, that is, two nodes were related if
their edit distance was equal to 1 or 2. Each node was characterized
with its degree, i.e., the number of links it shares with other words.

@@

We start by analysing word connectivity in the global (static) network.
We constructed this network using nouns at the oldest age for which we
have CDI data (e.g., in English this corresponds to the network by 30
months). This global netowrk is the end-state towards which both PAT and
PAC should converge by the last month of learning. Morover, following
Hills et al. (2009), we used this end-state netowrk as a proxy for the
external connectivity in the learning environment. Below we analyse
properties of this global networks that are relevant to PAT and/or PAC.

@@

Connectivity in the global network is directly related to PAC as it
represents the explicit criterion PAC uses to determine what words
should be learned first (Figure \ref{fig:growth}). Therefore, a direct
consequence of a PAC-like growth scenario is a correlation betweeen
connectivity in the global network and the age of
acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicity on external connectivity. Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).}
Figure \ref{fig:data_all} shows how the age of acquisition for each word
varies as a function of its connectivity/degree (or indegree for the
semantic network). For ease of visual comparison, the predictor (i.e.,
the degree) was centered and scaled across languages. The plots show,
overall, a negative correlation between the month of acquisition and the
degree, indicating that nouns with higher degrees are generally learned
earlier.

\subsubsection{Power law degree
distribution?}\label{power-law-degree-distribution}

We also analysed the global network's degree distribution. This property
is particularly relevant to PAT as this growth scenario is known to
generate networks with a power-law degree distribution (Barabasi \&
Albert, 1999). If the network displays this property, this fact would
strongly suggests a PAT-like generative process. Conversely, if the
degree distribution does not follow a power law, this fact would weaken
the case for PAT. The results are shown in Figure
\ref{fig:degree_distribution}. Overall, we did not find consistent
evidence for a power law distribution: the extent to which the degree
distribution approximates a power law varies across dimensions and
languages.

For a more direct test of the developmental process, we fit explicit
growth models to the data (next section).

@@

\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).}\label{fig:pred_ind_img}
\end{figure*}
\end{CodeChunk}

@@

To test the network growth scenarios, we fit different growth models to
the data. We proceeded as follows. We calculated the probability that a
word \(w_i\), with a growth value \(d_i\) would enter the lexicon at a
given month, using a softmax function:

@@

\noindent where \(\beta\) is a fitted parameter that captures the
magnitude of the relationship between network parameters and growth
(analogous to a regression coefficient). A positive value of \(\beta\)
means that words with higher growth values \(d_i\) are acquired first,
and a negative value means that words with lower growth values are
acquired first (see Figure \ref{fig:growth} for illustrations of growth
scenarios, and how a word's growth value \(d_i\) is defined in each of
these scenarios). The normalization includes all words that could be
learned at that month.

We estimated the parameter \(\beta\) using a Bayesian approach. The
inference was performed using the probabilistic programming language
WebPPL (N. Goodman \& Stuhlmüller, 2014). We defined a uniform prior
over \(\beta\), and at each month, we computed the likelihood function
over words that could possibly enter the lexicon at that month, fit to
the words that have been actually learned at that month (using formula
1). Markov chain monte carlo sampling resulted in a posterior
distribution over \(\beta\), which we summarized in Figure
\ref{fig:pred_ind}.

Besides fitting a growth model to the data, we conducted another
evaluation. This second evaluation consists in determining, in each
month, the growth value distribution of all words that could possibly be
learned at this month, and then computing the z-score of each learned
word with respect to this distribution. For each growth scenario, we
tested if the distribution constituted by the z-scores of all learned
words was different from zero, using a one-sample t-test.

@@

Above we evaluated the network growth scenarios individually. As a next
step, we analysed their relative contribution to the learning process.
This was done through adding more fitting parameters to the model, that
is, by substituting \(\beta d_i\) in formula (1) with:
\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
PhonoPAC. Using the same fitting technique, we obtained the values shown
in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
phonological and semantic networks contribute to lexical growth, but the
phonological network appears to be stronger and more consistent across
languages. In summary, the findings show that both semantic and
phonological networks contribute to the learning process, and that they
both grow primarily by PAC, relying on the external connectivity in the
learning environment, rather than the internal connectivity in the
acquired lexicon.

@@

\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language. Values above 0 indicate a positive relationship (e.g. longer words tend to have a higher AoA), while values below 0 indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA). Ranges indicate 95\% confidence intervals.}\label{fig:regressions_img}
\end{figure*}
\end{CodeChunk}

@@

We saw that the way semantic and phonological information is structured
in the learning environment (i.e., PAC) contribute to noun learning
across languages. However, we know that other factors influence learning
as well (e.g., Braginsky et al., 2016). Next we investigated how
semantic and phonological connectivity interact with two other factors.
The first one is word frequency, a well studied factor shown to predict
the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
2008). The second factor is word length, which correlates with
phonological connectivity.

Since PAT was uninformative, we dropped it from this analysis. Thus, we
no longer needed to fit the growth model month-by-month as in the
previous section. In fact, word utilities (i.e., growth values) in the
case of PAC are fixed, they do not depend on previously learned words. A
more direct way to assess and compare the contribution of PAC in
relation to other word-level factors is through conducting linear
regressions, where connectivity in the learning environment (at both the
phonological and semantic level), frequency and length predict the age
of acquisition.

We used the frequency estimates from Braginsky et al. (2016) where
unigram counts were derived based on CHILDES corpora in each language
(note that these frequency counts are based on transcripts from
independent sets of children and represent a general estimate of
environmental frequency across children). For each word, counts included
words that shared the same stem (e.g., cats counts as cat), or words
that were synonymous (e.g.~father counts as daddy). For word length, we
used our generated IPA transcription.

We conducted two analyses. We fit a linear regression for each language,
and we fit a linear mixed-effect to all the data pooled across
languages, with language as a random effect. Figure
\ref{fig:regressions_img} shows the coefficient estimate for each
predictor in each language, and Figure \ref{fig:regressions_all_img}
shows the coefficient estimates for all languages combined (all
predictors were centered and scaled). The findings were as follows.
Overall, frequency is the largest and most consistent predictor of age
of acquisition, replicating results for nouns across a variety of
analyses (Braginsky et al., 2016; J. C. Goodman et al., 2008; B. C. Roy
et al., 2015). Word length predicts learning in some languages such as
Croatian and Norwegian, but not in others (including English). It
remains, however, a significant predictor in the global model. As for
the factors of interest, i.e., semantic and phonological connectivity,
we also found cross-linguistic differences. The phonological
connectivity contributes to learning in languages such as Croatian,
English and Russian, whereas semantic connectivity contributes to
learning in Turkish, Spanish and to some extent in Croatian, but
interestingly not in
English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in Hills et al. 2009. However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates. Another important difference is the number of words tested: our study uses a larger set of nouns.}
Despite this cross-linguistic variation, both phonological and semantic
connectivity remain significant predictors in the global model.

@@

The present study provided a comprehensive analysis of how lexical
connectivity influences the age of acquisition of nouns in toddlers. We
compared two network growth scenarios and assessed their relative
contributions and the relative contributions of phonological
vs.~semantic networks across eight languages. One scenario, PAT,
described a ``rich get richer'' network growth model in which the
structure of the learner's internal network determines future growth;
the other, PAC, described a model in which the external, global
environmental network structure determines learners' growth patterns.
Part of the findings largely replicate the results obtained in Hills et
al. (2009), i.e., semantic networks (based on free associations) grow by
preferential acquisition, not by preferential attachment. Another
finding was that phonological networks also grow primarily by
preferential acquisition, especially when both scenarios (PAT and PAC)
were pitted against each other in the same model. These findings
generalize well across languages. Moreover, both semantic and
phonological connectivity in the learning environment (i.e., PAC)
predict growth in a consistent way across many languages. However, when
pitted against other known predictors of age of acquisition (word
frequency and length), the effect of word connectivity shows a
cross-linguistic variation, predicting learning in some languages, but
not in others. Despite this cross-linguistic variation, both
phonological and semantic connectivity contribute to the overall
learning (when data is pooled across languages).

@@

One important result of the study is that children start by learning
words that have high phonological and semantic similarity with a variety
of other words in the learning environment, not in the child's available
lexicon. This suggests that children are sensitive to connectivity even
without having first acquired the connected words. How can children
indirectly detect highly connected words, and why would such words be
more readily learned?

In the semantic case, free association can be predicted through the
patterns of word co-occurrence (Griffiths, Steyvers, \& Tenenbaum,
2007), meaning that highly connected words tend to be the words that
co-occur with many other words in various contexts. One possibility,
suggested by Hills et al. (2010), is that the referents of such words
are more easily disambiguated from other potential referents (because
their presence in mulitiple contexts provides more diambiguating
statisitcs about their true referents). (Smith \& Yu, 2008) showed that
children can disambiguate the words' referents based on such
cross-situational statisitics (Smith \& Yu, 2008).

>>>>

\begin{abstract}
Children tend to produce words earlier when they are connected to a
variety of other words along both the phonological and semantic
dimensions. Though this connectivity effect has been extensively
documented, little is known about the underlying developmental
mechanism. One view suggests that learning is primarily driven by a
network growth model where highly connected words in the child's early
lexicon attract similar words. Another view suggests that learning is
driven by highly connected word in the external learning environment
instead of highly connected words in the early internal lexicon. The
present study tests both scenarios systematically in both the
phonological and the semantic domains, and across 8 languages. We show
that external connectivity in the learning environment drives growth in
both the semantic and the phonological networks, and that this pattern
is consistent cross-linguistically. The findings suggest a word learning
mechanism where children harness their statistical learning abilities to
(indirectly) detect and learn highly connected words in the learning
environment.

@@

Besides these word-level properties, the lexical structure (that is, how
words relate to each other) also influences the age of acquisition of
words. The lexical structure is best characterized in terms of a network
where each node represents a word in the vocabulary, and each link
between two nodes represents a relationship between the corresponding
pair of words. Previous studies investigated early vocabulary networks
based on different word relations such as shared semantic features,
target-cue relationships in free association norms, co-occurrence in
child directed speech, and phonological similarity. These studies have
found that children tend to produce earlier the words that have higher
neighborhood density (i.e., high connectivity in the network) both at
the phonological and the semantic level (Engelthaler \& Hills, 2017;
Hills, Maouene, Riordan, \& Smith, 2010; Hills, Maouene, Maouene, Sheya,
\& Smith, 2009; Stella, Beckage, \& Brede, 2017; Storkel, 2009).

While most studies focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
Steyvers \& Tenenbaum (2005) suggested that the effect of connectivity
is the consequence of how the lexical network gets constructed in the
child's mind. According to this explanation, known as Preferential
Attachment (PAT), highly connected words in the child's lexicon tend to
``attract'' more words over time, in a rich-get-richer scenario
(Barabasi \& Albert, 1999). In other words, what predicts word learning
is the \emph{internal} connectivity in the child's early lexicon. In
contrast, Hills et al. (2009) suggested that what biases the learning is
not the connectivity in the child's internal lexicon but, rather,
\emph{external} connectivity in the learning environment. They called
this alternative explanation Preferential Acquisition (PAC). Figure
\ref{fig:growth} shows an illustration of both growth scenarios with the
same simplified network. These two proposals represent two divergent
ideas about the role of lexical networks in acquisition. On the PAT
proposal, network structure is a causal factor in early word learning;
in contrast, on the PAC approach, network structure is not internally
represented and, therefore, might be an epiphenomenon of the statistics
of the linguistic input (see discussion).

@@

\caption{\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
\end{figure}
\end{CodeChunk}

Studies that investigate lexical network growth have focused on semantic
networks using English data (Hills et al., 2010, 2009; Steyvers \&
Tenenbaum, 2005). The novelty of the current study is threefold: First,
it investigates whether phonological networks, like semantic networks,
grow by PAC, or if they rather grow by PAT. Second, it provides a
systematic comparison of both network growth scenarios in the
phonological and the semantic domains and assesses their relative
contribution to the learning process. Third, it tests the generality of
the findings across eight languages.

@@

\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
\end{figure*}
\end{CodeChunk}

@@

\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
\end{figure*}
\end{CodeChunk}

@@

We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
2017), an open repository aggregating cross-linguistic language
developmental data of the MacArthur-Bates Communicative Development
Inventory (CDI), a parent report vocabulary checklist. Parent report is
a reliable and valid measure of children's vocabulary that allows for
the cost-effective collection of datasets large enough to test
network-based models of acquisition (Fenson et al., 1994). We used the
\emph{Words and Sentence} version of the CDI which contains the
productive vocabulary of toddlers (age varied between 16 to 36 months).
Following previous studies (Hills et al., 2009; Storkel, 2009), we
restricted our analysis to the category of nouns. We defined the age of
acquisition of a given word by the month at which this word was produced
by at least 50\% of children (J. C. Goodman et al., 2008). We excluded
nouns that have not been learned (according to this criterion) by the
last month for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English,
Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
nouns that had entries in the Florida Association Norms (see below).
Since these norms are available only in English, we used the
hand-checked translation equivalents provided by Braginsky et al.
(2016), allowing us to use the English association norms across
languages. Table \ref{tab:stats} gives an overview of the data used.
Translation equivalents were originally constructed for a subset of
words appearing on the toddler CDI form, and so not all words are
currently available. Note, however, that all languages have at least
60\% of nouns translated.

@@

We constructed the semantic networks following the procedure outlined in
Hills et al. (2009). We used as an index of semantic relatedness the
Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
This dataset was collected by giving adult participants a word (the
cue), and asking them to write the first word that comes to mind (the
target). For example, when given the word ``ball'', they might answer
with the word ``game''. A pair of nodes were connected by a directed
link from the cue to the target if there was a cue-target relationship
between these nodes in the association norms. The connectivity of a
given node was characterized by its \emph{indegree}: the number of links
for which the word was the target. To model growth from month to month,
we constructed a different network at each month, made of the words that
have been acquired at that month.

@@

We generated approximate International Phonetic Alphabet (IPA)
transcriptions from the orthographic transcription, across languages,
using the open source text-to-speech software
\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
the Levenshtein distance (also known as edit distance) as a measure of
phonological relatedness between two nodes. The measure counts the
minimum number of operations (insertions, deletions, substitutions)
required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance
of 1 (e.g., Storkel, 2009). However, in these previous studies the
network was built using an adult vocabulary. However, since the
children's vocabulary contains very few word pairs with an edit distance
of 1, the resulting networks were too sparse and uninformative. Thus, we
increased the threshold from 1 to 2, that is, two nodes were related if
their edit distance was equal to 1 or 2. The connectivity of a given
node was characterized with its \emph{degree}: the number of links it
shares with other words.

@@

We start by analysing word connectivity in the global (static) network.
We constructed this network using nouns at the oldest age for which we
have CDI data (e.g., in English this corresponds to the network by 30
months). This global network is the end-state towards which both PAT and
PAC should converge by the last month of learning. Moreover, following
Hills et al. (2009), we used this end-state network as a proxy for the
external connectivity in the learning environment. Below we analyse
properties of this global networks that are relevant to PAT and/or PAC.

@@

Connectivity in the global network is directly related to PAC as it
represents the explicit criterion PAC uses to determine what words
should be learned first (Figure \ref{fig:growth}). Therefore, a direct
consequence of a PAC-like growth scenario is a correlation between
connectivity in the global network and the age of
acquisition.\footnote{Note that this correlation is also compatible with PAT, even if this growth scenario does not rely explicitly on external connectivity. Indeed, from a PAT perspective, higher connectivity in the global network is caused by earlier learning, i.e., some words end up being highly connected in the global network precisely because they happen to be acquired earlier (and therefore have a higher chance of forming more links over time).}
Figure \ref{fig:data_all} shows how the age of acquisition for each word
varies as a function of its degree (or indegree for the semantic
network). For ease of visual comparison, the predictor (i.e., the
degree) was centered and scaled across languages. The plots show,
overall, a negative correlation between the month of acquisition and the
degree, indicating that nouns with higher degrees are generally learned
earlier.

\subsubsection{Power-law degree
distribution?}\label{power-law-degree-distribution}

We also analysed the global network's degree distribution. This property
is particularly relevant to PAT as this growth scenario is known to
generate networks with a power-law degree distribution (i.e., a
distribution of the form \(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi
\& Albert, 1999). If the network displays this property, this fact would
suggests a PAT-like generative process. Conversely, if the degree
distribution does not follow a power law, this fact would weaken the
case for PAT. The log-log plots are shown in Figure
\ref{fig:degree_distribution}. We fit a discrete power law to each
empirical degree distribution following the procedure outlined in
Clauset, Shalizi, \& Newman (2009) and using the related R package
(poweRlaw, Gillespie, 2015). In brief, the analysis consists in two
steps. First, we derive the optimal cut-off, \(k_{min}\), above which
the distribution is more likely to follow a power
law\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.},
and we estimate the corresponding scaling parameter \(\alpha\). Second
we calculate the goodness-to-fit, which results in a \(p\)-value
quantifying the plausibility of the model. Overall, we did not find
strong evidence against a power-law distribution: the \(p\)-value was
generally above 0.1, except for the Italian phonological network where
we obtained \(p < 0.05\) (suggesting that the power law can be ruled out
in this particular case).

In sum, the static properties of the global network do not provide
conclusive evidence in favor or against any of the growth scenarios in
question. For a more direct test of the developmental process, we need
to fit explicit growth models to the data.

@@

\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:pred_ind_img}
\end{figure*}
\end{CodeChunk}

@@

To test the network growth scenarios, we fit different growth models to
the data. We calculated the probability that a word \(w_i\), with a
growth value \(d_i\) would enter the lexicon at a given month, using a
softmax function:

@@

\noindent where \(\beta\) is a fitted parameter that captures the
magnitude of the relationship between network parameters and growth
(analogous to a regression coefficient). A positive value of \(\beta\)
means that words with higher growth values \(d_i\) are acquired first,
and a negative value means that words with lower growth values are
acquired first (see Figure \ref{fig:growth} for an illustration of how
growth values \(d_i\) are defined in each growth scenario). The
normalization includes all words that could be learned at that month.

We estimated the parameter \(\beta\) using a Bayesian approach. The
inference was performed using the probabilistic programming language
WebPPL (N. Goodman \& Stuhlmüller, 2014). We defined a uniform prior
over \(\beta\), and at each month, we computed the likelihood function
over words that could possibly enter the lexicon at that month, fit to
the words that have been learned at that month (using formula 1). Markov
Chain Monte Carlo sampling resulted in a posterior distribution over
\(\beta\), which we summarized in Figure \ref{fig:pred_ind}.

Besides fitting a growth model to the data, we conducted a separate
evaluation. This second evaluation consists in determining, in each
month, the growth value distribution of all words that could possibly be
learned at this month, and then computing the z-score of each learned
word with respect to this distribution. For each growth scenario, we
tested if the distribution constituted by the z-scores of all learned
words was different from zero, using a one-sample t-test.

@@

Above we evaluated the network growth scenarios individually. As a next
step, we analysed their relative contribution to the learning process.
This was done through adding more fitted parameters to the model, that
is, by substituting \(\beta d_i\) in formula (1) with:
\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
PhonoPAC. Using the same fitting technique, we obtained the values shown
in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
phonological and semantic networks contribute to lexical growth, but the
phonological network appears to be stronger and more consistent across
languages. In summary, the findings show that both semantic and
phonological networks contribute to the learning process, and that they
both grow primarily by PAC, relying on the external connectivity in the
learning environment, rather than the internal connectivity in the
acquired lexicon.

@@

\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA).}\label{fig:regressions_img}
\end{figure*}
\end{CodeChunk}

@@

We saw that the way semantic and phonological information is structured
in the learning environment (i.e., PAC) contributes to noun learning
across languages. However, we know that other factors influence learning
as well (e.g., Braginsky et al., 2016). Next we investigated how
semantic and phonological connectivity interact with two other factors.
The first one is word frequency, a well studied factor shown to predict
the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
2008). The second factor is word length, which correlates with
phonological connectivity.

Since PAT was uninformative, we dropped it from this analysis, keeping
only PAC. This simplified the model because we no longer needed to fit
growth
month-by-month.\footnote{This was a requirement only for PAT whose utilities varied from month to month, depending on previously learned words.}
A more direct way to assess and compare the contribution of PAC in
relation to other word-level factors is through conducting linear
regressions, where connectivity in the learning environment, frequency
and length predict the age of acquisition.

We used the frequency estimates from Braginsky et al. (2016) where
unigram counts were derived based on CHILDES corpora in each
language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children}
For each word, counts included words that shared the same stem (e.g.,
cats counts as cat), or words that were synonymous (e.g.~father counts
as daddy). For word length, we used our generated IPA transcription.

We conducted two analyses. We fit a linear regression for each language,
and we fit a linear mixed-effect model to all the data pooled across
languages, with language as a random effect. Figure
\ref{fig:regressions_img} shows the coefficient estimate for each
predictor in each language, and Figure \ref{fig:regressions_all_img}
shows the coefficient estimates for all languages combined (all
predictors were centered and scaled). The findings were as follows.
Overall, frequency is the largest and most consistent predictor of age
of acquisition, replicating results for nouns across a variety of
analyses (Braginsky et al., 2016; J. C. Goodman et al., 2008; B. C. Roy
et al., 2015). Word length predicts learning in some languages such as
Croatian and Norwegian, but not in others (including English). It
remains, however, a significant predictor in the global model. As for
the factors of interest, i.e., semantic and phonological connectivity,
we also found cross-linguistic differences. Phonological connectivity
contributes to learning in languages such as Croatian, English and
Russian, whereas semantic connectivity contributes to learning in
Turkish, Spanish and to some extent in Croatian, but not in
English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in Hills et al. 2009. However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates. Another important difference is the number of words tested: our study uses a larger set of nouns.}
Despite this cross-linguistic variation, both phonological and semantic
connectivity remain significant predictors in the global model.

@@

The present study provided a comprehensive analysis of how lexical
connectivity influences the age of acquisition of nouns in toddlers. We
compared two network growth scenarios and assessed their relative
contributions across eight languages. One scenario, PAT, described a
``rich get richer'' network growth model in which the structure of the
learner's internal network determines future growth; the other, PAC,
described a model in which the external, global environmental network
structure determines learners' growth patterns. Part of the findings
largely replicates the results obtained in Hills et al. (2009), i.e.,
semantic networks (based on free associations) grow by preferential
acquisition, not by preferential attachment. A novel finding was that
phonological networks also grow primarily by preferential acquisition,
especially when both scenarios (PAT and PAC) were pitted against each
other in the same model. These findings generalize well across
languages. Moreover, both semantic and phonological connectivity in the
learning environment (i.e., PAC) predict growth in a consistent way
across many languages. Nevertheless, when pitted against other known
predictors of age of acquisition (word frequency and length), the effect
of word connectivity shows a cross-linguistic variation, predicting
learning in some languages, but not in others. Despite this
cross-linguistic variation, both phonological and semantic connectivity
contribute to the overall learning (when data is pooled across
languages).

@@

One important result of the study is that children start by learning
words that have high phonological and semantic similarity to a variety
of other words in the learning environment, not in the child's available
lexicon. This suggests that children are sensitive to connectivity even
without having first acquired the connected words. How can children
indirectly detect highly connected words, and why would such words be
more readily learned?

In the semantic case, free association can be predicted through the
patterns of word co-occurrence (Griffiths, Steyvers, \& Tenenbaum,
2007), meaning that highly connected words tend to be the words that
co-occur with many other words in various contexts. One possibility,
suggested by Hills et al. (2010), is that the referents of such words
are more easily disambiguated from other potential referents because
their presence in multiple contexts provides more cross-situational,
disambiguating statistics about their true referents (Smith \& Yu,
2008).

In the phonological case, connectivity is inherently correlated with
phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
is, highly connected words tend to be made of frequent sound sequences.
Even infants (whose vocabulary is still very rudimentary) show a
sensitivity for high frequency sound sequences in the ambient language
(Jusczyk, Luce, \& Charles-Luce, 1994). Moreover, phonotactic
probability facilitates learning and recognition (e.g., Storkel, 2001).
In other words, children's sensitivity to local phonotactic regularities
might lead them to learn higher-probability words more easily. This
learning effect, in turn, would lead to an observed pattern of growth
that would appear to follow the PAC growth model even though learners
themselves would only be tracking local statistics.

Finally, while validating previous results using network growth models,
our study suggests that these correlational patterns may emerge from the
operation of simpler mechanisms in both the semantic and phonological
domains. One question for future experimental work is whether such
patterns of growth can be produced in controlled behavioral experiments.
